One page description

### 2016-12-06 publications/Journal/5-hotswap.tex
* fixed image 3 capitalization of abbreviations * fixed image 12 title * fixed images 15-17 mentioning pdevs, using "inherent parallelism" instead * fixed images 19-21 - - -> also changed the rotation and scaling of image 19 back to what it should be had the .eps to .pdf converter of Latex not messed up earlier. * fixed images 26-27 --- note: on image 21, I haven't changed the style of the 0 lines into the regular red+dashed+arrow at the end because this was a quick Inkscape job.
* turned the pSim into a macro (\pSim) in case we might want to change the name. * replaced a few occurrences of PD

As usual, switching imposes an overhead and should thus only be done if the benefits outweigh the induced overhead.
This overhead depends on the size of the model and the number of simulation cores.
For a simple model and a few cores, the overhead is less than a second.

@@

\begin{figure*}
    \center
    \includegraphics[height=\textwidth, angle=-90 ]{fig/queue_allocation.eps}
    \caption{Queue model simulation trace across 4 kernels.}
    \label{fig:Queue_allocation}
\end{figure*}

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{Phold simulation trace for parallel simulation using three kernels.}
    \label{fig:phold_allocation}
\end{figure}

>>>>

As usual, switching imposes an overhead and should thus only be done if the benefits outweigh the induced overhead.
This overhead depends on the size of the model and the number of simulation cores.
For a simple model and a few cores, the overhead is less than a second. 
Creating new cores and moving the simulation models has a constant overhead linear in the amount of cores and models. The time required to synchronize and halt the existing cores is variable, especially if the old synchronization protocol is optimistic since there is no real limit on the virtual time difference between cores. Given that the existing cores are equally loaded, this time difference will in practice scale linearly with the number of cores.

@@

\begin{figure*}
    \center
    \includegraphics[width=\textwidth ]{fig/queue_allocation.eps}
    \caption{Queue model simulation trace across 4 kernels.}
    \label{fig:Queue_allocation}
\end{figure*}

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth]{fig/phold_parallel_allocation.eps}
    \caption{Phold simulation trace for multi core simulation using three kernels.}
    \label{fig:phold_allocation}
\end{figure}
